The challenge and promise of software citation for credit, identification, discovery, and reuse

### 2016-04-07 SC-challenge.tex
added new line to quotation
Adding some background about indexing

\knnote{be more specific about related work targeting challenges}

>>>>

Even if there were an adopted, standard method for software citation there is currently a distinct lack of support for indexing any such citations by indexers (e.g., Web of Science, Scopus, Google Scholar). One possible exception to this is within the astrophysics community where indexing of citations is also carried out by an independent, community run service (NASA ADS ~\cite{nasaads}). NASA ADS already index references to software listed in the Astrophysics Source Code Library~\cite{ascl} and following a AAS/GitHub sponsored meeting in 2015 ~\cite{aas-software-index} made a committment to expand upon this functionality.
